---
title: "Improving Vaccine Distribution with Graph Networks"
author: "STAT 636 Final Project "
date: "`r Sys.Date()`"
runtime: shiny
output:
  html_document:
    toc: true
    toc_depth: 3
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Step 0 – Libraries and Options

```{r libraries}
library(tidyverse)
library(janitor)
library(lubridate)
library(sf)
library(tigris)
library(igraph)
library(tidygraph)
library(ggraph)
library(shiny)
library(leaflet)
library(DT)

options(tigris_use_cache = TRUE, tigris_class = "sf")
```

# Step 1 – Import and Clean CDC Vaccination Data

## Step 1.1 – Read the CSV

```{r import-data}
vax_raw <- read_csv("DATA.csv") %>%
  clean_names()

print("Raw vaccination data (first rows):")
print(head(vax_raw))

print("Column names:")
print(names(vax_raw))
```

## Step 1.2 – Basic Cleaning and Latest Snapshot

```{r clean-latest}
vax <- vax_raw %>%
  transmute(
    date = mdy(date),                  # from "05/10/23" format
    fips = str_pad(fips, 5, pad = "0"),
    recip_county,
    recip_state,
    completeness_pct,
    series_complete_pop_pct,
    booster_doses_vax_pct,
    svi_ctgy,
    metro_status,
    census2019,
    census2019_5plus_pop,
    census2019_18plus_pop,
    census2019_65plus_pop
  ) %>%
  filter(!is.na(fips), !is.na(date))

latest_date <- max(vax$date, na.rm = TRUE)
latest_date

vax_latest <- vax %>%
  filter(date == latest_date)

cat("Imported vaccination data with", nrow(vax_latest), "rows for", latest_date, "\n")
print(head(vax_latest))
```

# Step 2 – Geographic Data (County Shapefiles)

## Step 2.1 – Download and Prepare County Shapefiles

```{r shapefiles}
counties_sf <- counties(cb = TRUE, year = 2021) %>%
  st_transform(4326) %>%
  mutate(geoid = str_pad(GEOID, 5, pad = "0"))

county_vax <- counties_sf %>%
  left_join(vax_latest, by = c("geoid" = "fips"))

cat("Merged shapefile and vaccination data; rows:", nrow(county_vax), "\n")
cat("Rows with missing vaccination %:", sum(is.na(county_vax$series_complete_pop_pct)), "\n")
```

# Step 3 – Build County Adjacency Network

## Step 3.1 – Compute Adjacency and Edge List

```{r adjacency}
adj_list <- st_touches(county_vax)

edge_df <- purrr::map2_dfr(
  .x = seq_along(adj_list),
  .y = adj_list,
  ~ tibble(
    from = county_vax$geoid[.x],
    to   = county_vax$geoid[.y]
  )
) %>%
  filter(!is.na(from), !is.na(to), from != to) %>%
  distinct()

cat("Edges before filtering:", nrow(edge_df), "\n")

vertices <- county_vax %>%
  st_drop_geometry() %>%
  transmute(
    geoid = geoid,
    name  = geoid,                 # igraph vertex id
    recip_county,
    recip_state,
    date,
    completeness_pct,
    series_complete_pop_pct,
    booster_doses_vax_pct,
    svi_ctgy,
    metro_status,
    census2019,
    census2019_5plus_pop,
    census2019_18plus_pop,
    census2019_65plus_pop
  ) %>%
  filter(!is.na(name)) %>%
  distinct(name, .keep_all = TRUE)

stopifnot(!anyDuplicated(vertices$name))

edge_df <- edge_df %>%
  filter(from %in% vertices$name, to %in% vertices$name)

cat("Final vertices:", nrow(vertices), "\n")
cat("Final edges:", nrow(edge_df), "\n")
```

## Step 3.2 – Build igraph / tidygraph Object

```{r build-graph}
g <- graph_from_data_frame(d = edge_df, vertices = vertices, directed = FALSE)
print(g)

g_tbl <- as_tbl_graph(g)
print(g_tbl)
```

# Step 4 – Node Features and Neighbour Metrics

## Step 4.1 – Create Node-Level Features

```{r node-features}
g_tbl <- g_tbl %>%
  mutate(
    vax_pct          = series_complete_pop_pct,
    booster_pct      = booster_doses_vax_pct,
    svi_category     = svi_ctgy,
    metro_status     = metro_status,
    pop_total        = census2019,
    pop_5plus        = census2019_5plus_pop,
    pop_18plus       = census2019_18plus_pop,
    pop_65plus       = census2019_65plus_pop
  )

print("Node features (first rows):")
g_tbl %>%
  as_tibble() %>%
  select(name, recip_county, recip_state, vax_pct, booster_pct, pop_total) %>%
  head() %>%
  print()
```

## Step 4.2 – Neighbour-Based Vaccination Metrics

```{r neighbour-metrics}
g_igraph <- as.igraph(g_tbl)

vax_vec <- g_tbl %>% as_tibble() %>% pull(vax_pct)
names(vax_vec) <- g_tbl %>% as_tibble() %>% pull(name)

neigh_list <- ego(g_igraph, order = 1, nodes = V(g_igraph), mode = "all")

neigh_mean_vax <- purrr::map_dbl(neigh_list, function(nb) {
  ids <- names(nb)
  mean(vax_vec[ids], na.rm = TRUE)
})

g_tbl <- g_tbl %>%
  mutate(neighbour_mean_vax = neigh_mean_vax)

print("Neighbour-based vaccination metrics (first rows):")
g_tbl %>%
  as_tibble() %>%
  select(name, vax_pct, neighbour_mean_vax) %>%
  head() %>%
  print()
```

# Step 5 – Centrality and Community Structure

## Step 5.1 – Centrality Metrics

```{r centrality}
g_tbl <- g_tbl %>%
  mutate(
    degree     = centrality_degree(),
    betweenness = centrality_betweenness(),
    closeness   = centrality_closeness()
  )

print("Centrality metrics (first rows):")
g_tbl %>%
  as_tibble() %>%
  select(name, degree, betweenness, closeness) %>%
  head() %>%
  print()
```

## Step 5.2 – Community Detection (Louvain)

```{r communities}
g_tbl <- g_tbl %>%
  mutate(community = as.factor(group_louvain()))

print("Top communities by size:")
g_tbl %>%
  as_tibble() %>%
  count(community) %>%
  arrange(desc(n)) %>%
  head() %>%
  print()
```

## Step 5.3 – Network Statistics

```{r stats}
g_igraph <- as.igraph(g_tbl)

graph_stats <- tibble(
  num_vertices    = gorder(g_igraph),
  num_edges       = gsize(g_igraph),
  density         = edge_density(g_igraph),
  diameter        = diameter(g_igraph, directed = FALSE, weights = NA),
  avg_path_length = mean_distance(g_igraph, directed = FALSE),
  num_components  = components(g_igraph)$no
)

print("Overall network statistics:")
print(graph_stats)
```

# Step 6 – Join Graph Features Back to Geometry for Mapping

```{r join-geometry}
nodes_features <- g_tbl %>%
  as_tibble() %>%
  select(
    name,
    recip_county,
    recip_state,
    vax_pct,
    booster_pct,
    neighbour_mean_vax,
    degree,
    betweenness,
    closeness,
    svi_category,
    metro_status,
    pop_total,
    pop_5plus,
    pop_18plus,
    pop_65plus,
    community
  )

county_graph_sf <- county_vax %>%
  left_join(nodes_features, by = c("geoid" = "name")) %>%
  mutate(
    recip_county = dplyr::coalesce(recip_county.x, recip_county.y),
    recip_state  = dplyr::coalesce(recip_state.x,  recip_state.y)
  ) %>%
  select(
    -recip_county.x, -recip_county.y,
    -recip_state.x,  -recip_state.y
  ) %>%
  filter(!is.na(vax_pct))
```

# Step 7 – Export Clean Nodes and Edges for GNN

```{r export-gnn}
nodes_for_gnn <- nodes_features %>%
  rename(node_id = name)

edges_for_gnn <- edge_df %>%
  transmute(
    src = from,
    dst = to
  )

write_csv(nodes_for_gnn, "nodes_for_gnn.csv")
write_csv(edges_for_gnn, "edges_for_gnn.csv")

cat("Exported", nrow(nodes_for_gnn), "nodes and", nrow(edges_for_gnn), "edges for modeling.\n")
```

# Step 8 – Shiny Dashboard UI (8 Sections)

```{r shiny-dashboard, echo=FALSE}
# Step 8 – Shiny Dashboard UI (8 Sections)

# Build nodes_df for UI
nodes_df <- nodes_features %>%
  arrange(recip_state, recip_county)

# Safe degree range for slider
deg_min <- min(nodes_df$degree, na.rm = TRUE)
deg_max <- max(nodes_df$degree, na.rm = TRUE)
if (!is.finite(deg_min)) deg_min <- 0
if (!is.finite(deg_max)) deg_max <- max(nodes_df$degree, na.rm = TRUE)
if (!is.finite(deg_max)) deg_max <- 10

# Optional GNN results
gnn_results <- NULL
if (file.exists("gnn_results.csv")) {
  gnn_results <- read_csv("gnn_results.csv", show_col_types = FALSE)
  nodes_df <- nodes_df %>%
    left_join(gnn_results, by = c("name" = "node_id"))
  county_graph_sf <- county_graph_sf %>%
    left_join(gnn_results, by = c("geoid" = "node_id"))
}

ui <- navbarPage(
  title = div(
    style = "display:flex; align-items:center; gap:10px;",
    span("US County Vaccine Network Dashboard", style = "font-weight:600;"),
    span("– STAT 636 : APPLIED MULTIVARIATE ANALYSIS ", style = "font-size:0.8em; color:#e0e0e0;")
  ),
  header = tagList(
    tags$head(
      tags$style(HTML("
        body {
          background-color: #f7f7f7;
        }
        .navbar-default {
          background-color: #1b4965;
          border-color: #1b4965;
        }
        .navbar-default .navbar-brand,
        .navbar-default .navbar-nav > li > a {
          color: #f8f9fa !important;
        }
        .navbar-default .navbar-nav > .active > a,
        .navbar-default .navbar-nav > .active > a:focus,
        .navbar-default .navbar-nav > .active > a:hover {
          background-color: #ffb703 !important;
          color: #003049 !important;
        }
        .navbar-default .navbar-nav > li > a:hover {
          background-color: #264653 !important;
          color: #f8f9fa !important;
        }
        .well, .panel {
          background-color: #ffffff !important;
          border-radius: 8px !important;
          border: 1px solid #e0e0e0 !important;
        }
      "))
    )
  ),

  # 1. County Explorer ------------------------------------------------------
  tabPanel("1. County Explorer",
           sidebarLayout(
             sidebarPanel(
               h4("Filter counties"),
               selectInput(
                 "state_sel",
                 "Select state:",
                 choices  = sort(unique(nodes_df$recip_state)),
                 selected = "TX"
               ),
               uiOutput("county_sel_ui"),
               sliderInput(
                 "degree_range",
                 "Filter by degree (number of neighbours):",
                 min   = deg_min,
                 max   = deg_max,
                 value = c(deg_min, deg_max)
               ),
               br(),
               helpText("Use the filters above to explore individual counties and their network context.")
             ),
             mainPanel(
               h3("County overview"),
               DTOutput("county_table"),
               br(),
               fluidRow(
                 column(6,
                        h4("State-wide vaccination % distribution"),
                        plotOutput("state_hist", height = 250)
                 ),
                 column(6,
                        h4("Degree vs vaccination % (selected state)"),
                        plotOutput("state_scatter", height = 250)
                 )
               )
             )
           )),

  # 2. Spatial Map ----------------------------------------------------------
  tabPanel("2. Spatial Map",
           sidebarLayout(
             sidebarPanel(
               h4("Spatial patterns"),
               selectInput(
                 "map_metric",
                 "Map metric:",
                 choices = c(
                   "Vaccination % (series_complete)" = "vax_pct",
                   "Booster % "                      = "booster_pct",
                   "Neighbour mean vaccination %"    = "neighbour_mean_vax"
                 ),
                 selected = "vax_pct"
               ),
               checkboxInput("map_focus_state", "Filter to a single state", value = FALSE),
               conditionalPanel(
                 condition = "input.map_focus_state == true",
                 selectInput(
                   "map_state",
                   "State for map:",
                   choices = sort(unique(nodes_df$recip_state)),
                   selected = "TX"
                 )
               ),
               br(),
               helpText("Hover over a county to see its name and vaccination percentage.")
             ),
             mainPanel(
               leafletOutput("vax_map", height = 600)
             )
           )),

  # 3. Network Graph --------------------------------------------------------
  tabPanel("3. Network Graph",
           sidebarLayout(
             sidebarPanel(
               h4("Network view"),
               selectInput(
                 "graph_color_by",
                 "Color nodes by:",
                 choices = c(
                   "Vaccination %" = "vax_pct",
                   "Booster %"     = "booster_pct",
                   "Degree"        = "degree",
                   "Community"     = "community"
                 ),
                 selected = "community"
               ),
               sliderInput(
                 "graph_sample",
                 "Subsample nodes for plotting:",
                 min   = min(500, nrow(nodes_df)),
                 max   = nrow(nodes_df),
                 value = min(2000, nrow(nodes_df)),
                 step  = 100
               ),
               br(),
               helpText("Subsample nodes to keep the layout readable.")
             ),
             mainPanel(
               h3("Force-directed county network"),
               plotOutput("graph_plot", height = 600)
             )
           )),

  # 4. Feature Explorer -----------------------------------------------------
  tabPanel("4. Feature Explorer",
           sidebarLayout(
             sidebarPanel(
               h4("Feature relationships"),
               selectInput(
                 "feat_x",
                 "X-axis:",
                 choices = c(
                   "Degree"                        = "degree",
                   "Vaccination % (vax_pct)"       = "vax_pct", 
                   "Booster % (booster_pct)"       = "booster_pct",
                   "Neighbour mean vax"            = "neighbour_mean_vax",
                   "Population total"              = "pop_total"
                 ),
                 selected = "degree"
               ),
               selectInput(
                 "feat_y",
                 "Y-axis:",
                 choices = c(
                   "Vaccination % (vax_pct)"       = "vax_pct",
                   "Booster % (booster_pct)"       = "booster_pct",
                   "Neighbour mean vax"            = "neighbour_mean_vax"
                 ),
                 selected = "vax_pct"
               ),
               selectInput(
                 "feat_color",
                 "Color by:",
                 choices = c(
                   "None"          = "none",
                   "SVI category"  = "svi_category",
                   "Metro status"  = "metro_status",
                   "Community"     = "community"
                 ),
                 selected = "none"
               )
             ),
             mainPanel(
               h3("Scatterplot of node-level features"),
               plotOutput("feature_scatter", height = 400),
               br(),
               h4("Distribution of vaccination %"),
               plotOutput("feature_hist", height = 250)
             )
           )),

  # 5. Model & Forecast -----------------------------------------------------
  tabPanel("5. Model & Forecast",
           sidebarLayout(
             sidebarPanel(
               h4("Simple forecasting models"),
               helpText("Compare a non-network baseline model with a network-aware model using neighbour_mean_vax."),
               sliderInput(
                 "train_frac",
                 "Training fraction:",
                 min   = 0.5,
                 max   = 0.9,
                 value = 0.8,
                 step  = 0.05
               ),
               actionButton("run_models", "Run models")
             ),
             mainPanel(
               h3("Model performance"),
               tableOutput("model_perf_table"),
               br(),
               h4("Predicted vs actual vaccination % (network-aware model)"),
               plotOutput("model_scatter", height = 350)
             )
           )),

  # 6. Unobserved Counties Simulator ---------------------------------------
  tabPanel("6. Unobserved Counties",
           sidebarLayout(
             sidebarPanel(
               h4("Simulate missing counties"),
               helpText("Hide a fraction of counties and compare global-mean vs neighbour-mean predictions."),
               sliderInput(
                 "hide_frac",
                 "Fraction of counties treated as unobserved:",
                 min   = 0.1,
                 max   = 0.5,
                 value = 0.2,
                 step  = 0.05
               ),
               actionButton("run_sim", "Run simulation")
             ),
             mainPanel(
               h3("Simulation results"),
               tableOutput("sim_table"),
               br(),
               h4("Error distribution for hidden counties"),
               plotOutput("sim_hist", height = 350)
             )
           )),

  # 7. Insights & Summary ---------------------------------------------------
  tabPanel("7. Insights & Summary",
           fluidPage(
             h3("Key insights from the network-based analysis"),
             tags$ul(
               tags$li("The county-level adjacency network reveals strong regional clustering in vaccination."),
               tags$li("Neighbour mean vaccination is a strong predictor of a county's own coverage."),
               tags$li("Network-aware models outperform non-network baselines when predicting vaccination levels."),
               tags$li("The exported node and edge files are ready for graph neural network (GNN) experiments.")
             ),
             br(),
             h4("Takeaway"),
             p("Incorporating county network structure transforms this into a spatial-graph forecasting problem, where graph-aware models like GNNs can leverage neighbour information to improve predictions for under-reported or unobserved counties.")
           )),

  # 8. Downloads ------------------------------------------------------------
  tabPanel("8. Downloads",
           fluidPage(
             h3("Exported data for further modeling"),
             p("These files can be used in Python (e.g., PyTorch Geometric, DGL) or R for advanced GNN experiments."),
             br(),
             downloadButton("dl_nodes", "Download nodes_for_gnn.csv"),
             br(), br(),
             downloadButton("dl_edges", "Download edges_for_gnn.csv")
           ))
)

server <- function(input, output, session) {

  # 1. County Explorer ------------------------------------------------------
  output$county_sel_ui <- renderUI({
    req(input$state_sel)
    counties_state <- nodes_df %>%
      filter(recip_state == input$state_sel) %>%
      arrange(recip_county)

    selectInput(
      "county_sel",
      "Select county:",
      choices  = unique(counties_state$recip_county),
      selected = unique(counties_state$recip_county)[1]
    )
  })

  filtered_state <- reactive({
    nodes_df %>%
      filter(
        recip_state == input$state_sel,
        degree >= input$degree_range[1],
        degree <= input$degree_range[2]
      )
  })

  output$county_table <- renderDT({
    req(input$county_sel)
    df <- filtered_state() %>%
      filter(recip_county == input$county_sel) %>%
      select(
        State                    = recip_state,
        County                   = recip_county,
        `Vaccination %`          = vax_pct,
        `Booster %`              = booster_pct,
        `Neighbour mean vax %`   = neighbour_mean_vax,
        Degree                   = degree,
        Betweenness              = betweenness,
        Closeness                = closeness,
        `Total population`       = pop_total,
        SVI                      = svi_category,
        `Metro status`           = metro_status,
        Community                = community
      )
    datatable(df, options = list(dom = "t", paging = FALSE))
  })

  output$state_hist <- renderPlot({
    df <- filtered_state()
    hist(df$vax_pct,
         main = paste("Vaccination % in", input$state_sel),
         xlab = "Series complete population %")
  })

  output$state_scatter <- renderPlot({
    df <- filtered_state()
    plot(df$degree, df$vax_pct,
         xlab = "Degree",
         ylab = "Vaccination %",
         main = paste("Degree vs Vaccination % in", input$state_sel))
  })

  # 2. Spatial Map ----------------------------------------------------------
  output$vax_map <- renderLeaflet({
    df <- county_graph_sf
    if (isTRUE(input$map_focus_state)) {
      df <- df %>% filter(recip_state == input$map_state)
    }

    if (nrow(df) == 0) {
      return(leaflet() %>% addTiles())
    }

    df <- df %>% st_transform(4326)

    metric <- input$map_metric
    if (!metric %in% names(df)) {
      metric <- "vax_pct"
    }

    df$map_value <- df[[metric]]

    pal_col <- colorNumeric("YlGnBu", domain = df$map_value, na.color = "#f0f0f0")

    leaflet(df) %>%
      addProviderTiles("CartoDB.Positron") %>%
      addPolygons(
        fillColor = ~ pal_col(map_value),
        color     = "#444444",
        weight    = 0.3,
        opacity   = 1,
        fillOpacity = 0.7,
        highlightOptions = highlightOptions(weight = 1.5, color = "#666", bringToFront = TRUE),
        label = ~ paste0(recip_county, ", ", recip_state, "<br>",
                         "Vax %: ", round(vax_pct, 1)),
        labelOptions = labelOptions(direction = "auto")
      ) %>%
      addLegend(
        pal    = pal_col,
        values = df$map_value,
        title  = metric,
        opacity = 0.7
      )
  })

  # 3. Network Graph --------------------------------------------------------
  output$graph_plot <- renderPlot({
    req(input$graph_sample, input$graph_color_by)
    set.seed(123)

    tryCatch({
      g_full   <- as.igraph(g_tbl)
      all_ids  <- V(g_full)$name
      n_sample <- min(input$graph_sample, length(all_ids))
      keep_ids <- if (n_sample < length(all_ids)) sample(all_ids, n_sample) else all_ids
      g_sub    <- induced_subgraph(g_full, vids = match(keep_ids, all_ids))

      if (gorder(g_sub) == 0) {
        plot.new(); text(0.5, 0.5, "No nodes available after sampling/filtering", cex = 1.1)
        return(invisible(NULL))
      }

      g_sub_tbl <- as_tbl_graph(g_sub)
      node_df   <- as_tibble(g_sub_tbl, active = "nodes")

      color_var <- input$graph_color_by
      if (!color_var %in% names(node_df)) {
        color_var <- "degree"
      }

      p <- ggraph(g_sub_tbl, layout = "fr") +
        geom_edge_link(alpha = 0.05) +
        geom_node_point(aes_string(color = color_var), size = 1.5) +
        theme_void() +
        labs(
          title = "County Vaccine Network — Force-directed layout",
          subtitle = paste0(
            "Nodes: ", gorder(g_sub_tbl),
            " | Edges: ", gsize(as.igraph(g_sub_tbl)),
            " | Color: ", color_var
          )
        )

      print(p)

    }, error = function(e) {
      plot.new()
      text(0.5, 0.5, paste("Plot error:", conditionMessage(e)), cex = 1, col = "red")
    })
  })

  # 4. Feature Explorer -----------------------------------------------------
  output$feature_scatter <- renderPlot({
    df    <- nodes_df
    xvar  <- input$feat_x
    yvar  <- input$feat_y
    colvar <- input$feat_color

    if (!xvar %in% names(df) || !yvar %in% names(df)) {
      plot.new(); text(0.5, 0.5, "Selected variables not found", col = "red"); return()
    }

    if (colvar == "none" || !colvar %in% names(df)) {
      plot(df[[xvar]], df[[yvar]],
           xlab = xvar,
           ylab = yvar,
           main = paste(yvar, "vs", xvar))
    } else {
      cols <- as.factor(df[[colvar]])
      plot(df[[xvar]], df[[yvar]],
           xlab = xvar,
           ylab = yvar,
           col  = cols,
           pch  = 16,
           main = paste(yvar, "vs", xvar, "colored by", colvar))
      legend("topright", legend = levels(cols), col = 1:length(levels(cols)),
             pch = 16, cex = 0.7)
    }
  })

  output$feature_hist <- renderPlot({
    hist(nodes_df$vax_pct,
         main = "Distribution of vaccination % across all counties",
         xlab = "Vaccination %")
  })

  # 5. Model & Forecast (simple models in R) --------------------------------
  observeEvent(input$run_models, {
    df <- nodes_df %>%
      filter(!is.na(vax_pct),
             !is.na(booster_pct),
             !is.na(neighbour_mean_vax))

    set.seed(123)
    n       <- nrow(df)
    train_n <- floor(input$train_frac * n)
    idx     <- sample(seq_len(n), size = train_n)

    train_df <- df[idx, ]
    test_df  <- df[-idx, ]

    baseline_mod <- lm(vax_pct ~ booster_pct + svi_category + metro_status + pop_total,
                       data = train_df)
    baseline_pred <- predict(baseline_mod, newdata = test_df)

    network_mod <- lm(vax_pct ~ booster_pct + svi_category + metro_status + pop_total + neighbour_mean_vax,
                      data = train_df)
    network_pred <- predict(network_mod, newdata = test_df)

    rmse <- function(truth, pred) sqrt(mean((truth - pred)^2, na.rm = TRUE))
    baseline_rmse <- rmse(test_df$vax_pct, baseline_pred)
    network_rmse  <- rmse(test_df$vax_pct, network_pred)

    perf_tbl <- tibble(
      Model = c("Baseline (no network)", "Network-aware (with neighbour_mean_vax)"),
      RMSE  = c(baseline_rmse, network_rmse)
    )

    output$model_perf_table <- renderTable(perf_tbl, digits = 3)

    output$model_scatter <- renderPlot({
      plot(test_df$vax_pct, network_pred,
           xlab = "Actual vaccination %",
           ylab = "Predicted vaccination % (network-aware)",
           main = "Predicted vs actual (network-aware model)")
      abline(0, 1, col = "red", lwd = 2)
    })
  })

  # 6. Unobserved Counties Simulator ----------------------------------------
  observeEvent(input$run_sim, {
    df <- nodes_df %>%
      filter(!is.na(vax_pct))

    set.seed(42)
    n       <- nrow(df)
    hide_n  <- floor(input$hide_frac * n)
    hidden_idx <- sample(seq_len(n), size = hide_n)

    df_hidden <- df[hidden_idx, ]
    df_obs    <- df[-hidden_idx, ]

    baseline_pred <- rep(mean(df_obs$vax_pct, na.rm = TRUE), nrow(df_hidden))

    vax_vec_all <- df$vax_pct
    names(vax_vec_all) <- df$name
    g_all <- as.igraph(g_tbl)
    neigh_list_all <- ego(g_all, order = 1, nodes = df_hidden$name, mode = "all")
    network_pred <- purrr::map_dbl(neigh_list_all, function(nb) {
      ids <- names(nb)
      mean(vax_vec_all[ids], na.rm = TRUE)
    })

    rmse <- function(truth, pred) sqrt(mean((truth - pred)^2, na.rm = TRUE))
    baseline_rmse <- rmse(df_hidden$vax_pct, baseline_pred)
    network_rmse  <- rmse(df_hidden$vax_pct, network_pred)

    sim_tbl <- tibble(
      Model = c("Baseline (global mean)", "Network smoother (neighbour mean)"),
      RMSE  = c(baseline_rmse, network_rmse)
    )

    output$sim_table <- renderTable(sim_tbl, digits = 3)

    output$sim_hist <- renderPlot({
      err_base <- df_hidden$vax_pct - baseline_pred
      err_net  <- df_hidden$vax_pct - network_pred

      hist(err_base,
           col = rgb(1, 0, 0, 0.4),
           xlab = "Prediction error (actual - predicted)",
           main = "Error distribution for hidden counties")
      hist(err_net,
           col = rgb(0, 0, 1, 0.4),
           add = TRUE)
      legend("topright",
             legend = c("Baseline", "Network smoother"),
             fill   = c(rgb(1, 0, 0, 0.4), rgb(0, 0, 1, 0.4)))
    })
  })

  # 8. Downloads ------------------------------------------------------------
  output$dl_nodes <- downloadHandler(
    filename = function() "nodes_for_gnn.csv",
    content = function(file) {
      write_csv(nodes_for_gnn, file)
    }
  )

  output$dl_edges <- downloadHandler(
    filename = function() "edges_for_gnn.csv",
    content = function(file) {
      write_csv(edges_for_gnn, file)
    }
  )
}

shinyApp(ui, server)
```

